Analysis plan

### 2023-01-23 02. Design/MSG-P2312-Analysis Plan.rmd
Update MSG-P2312-Analysis Plan.rmd
Adding some more details to data structure

---
title: "Analysis plan"
# date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Sara Guenther and Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(oescolorrrs)
library(oesrrr)
```

@@

The U.S. General Services Administration’s FY 2022 Annual Evaluation Plan includes evaluation goals that involve The Future of Work projects and objectives. This initiative is part of an effort to right-size the federal real estate footprint. Specifically, this project will examine the effects of distributed, virtual, and asynchronous work with the goal of informing future changes to interior space planning and building operations. We will join GSA telework rates and facility occupancy patterns with GSA roster data and describe rates of telework and on site work across employment and personal demographics. We will also determine the rates at which teams work together onsite, remotely, or in a hybrid environment.

@@

We will use Daily Check-In data obtained from Management Science and Innovation (MSI), a firm contracted to collect and maintain these data. We will merge in additional variables from the GSA Roster obtained from D2D. The GSA roster is updated monthly at the end of each month. [We currently have Nov 2022 and Dec 2022 updates; I will try to track down past months. Ideally, we will merge in each monthly check-in file with the preceding month’s roster file.]

@@

@@

@@

>>>>

---
title: "Analysis plan"
# date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Sara Guenther and Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(oescolorrrs)
library(oesrrr)
library(flextable)
```

@@

The U.S. General Services Administration's FY 2022 Annual Evaluation
Plan includes evaluation goals that involve The Future of Work projects
and objectives. This initiative is part of an effort to right-size the
federal real estate footprint. Specifically, this project will examine
the effects of distributed, virtual, and asynchronous work with the goal
of informing future changes to interior space planning and building
operations. We will join GSA telework rates and facility occupancy
patterns with GSA roster data and describe rates of telework and on site
work across employment and personal demographics. We will also determine
the rates at which teams work together onsite, remotely, or in a hybrid
environment.

@@

We will use Daily Check-In data obtained from Management Science and
Innovation (MSI), a firm contracted to collect and maintain these data.
We will merge in additional variables from the GSA Roster obtained from
D2D. The GSA roster is updated monthly at the end of each month. [We
currently have Nov 2022 and Dec 2022 updates; I will try to track down
past months. Ideally, we will merge in each monthly check-in file with
the preceding month's roster file.]

@@

For much of this study, no particular outcome will be analyzed. For
cluster and categorization, we will use various measures of staff work
location and frequency, for example, proportion of time teleworking or
frequency of teleworking on particular days. For sequence analysis, we
will use work status on particular days for staff or in combination with
team members.

@@

For all analysis, we will used a defined cohort of staff to examine work
status over period of time. A cohort of staff employed in the month of
March 2022 will be followed over six months. Teams will be defined by
the supervisors of groups of staff in the beginning of March 2022. Any
analysis will conduct may be reproduced on a separate cohort or may be
combined with multiple cohorts depending on the data availability.

The analysis can be thought of as a two-by-two box.

```{r, echo=FALSE}
tbl <- 
  tibble::tibble(level = rep("Level of analysis",2),
                      Group = c("Staff", "Team"),
                      Cluster = c("Person level aggregation of work status", "Team level aggregation of work status"),
                      Sequence = c("Daily person work status", "Daily team work status")
                       )
```

```{r}
tbl %>% 
  flextable() %>% 
  add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
  set_header_labels(level = "") %>% 
  merge_h(part = "header") %>% 
  merge_v(j = 1) %>% 
  theme_vanilla() %>% 
  autofit()
```

For cluster analysis of staff work status, the data will be transformed
so that each row is one staff person. From the raw data, the following
variables will be defined:

-   Proportion of days working onsite

-   Proportion of days working remote

-   Proportion of days working remote by the day of the week

-   Correlation of work status between days of the week

-   Indicator for an exit form employment

-   Indicator for a switch in supervisor

-   Size of team over observation window

For cluster analysis of team work status, the data will be transformed
so that each row is one team as defined by the supervisor. Supervisors
may be in multiple teams as supervisor and subordinate. From the raw
data, the following variables will be defined:

-   Size of team over observation window

-   Proportion of staff days working onsite

-   Proportion of staff days working remote

-   Proportion of staff days working remote by the day of the week

-   Proportion of days of staff concurrent remote status

-   Proportion of days of staff concurrent onsite status

-   Proportion of staff exiting team

@@

Proportion in staff time telework

Proportion in staff time telework by the day of the week

Proportion in staff time onsite

Proportion in staff time onsite by the day of the week

Correlations of by staff time between the days of the week

Size of teams
